\tool: Revisiting BadUSB with Type-C

### 2021-03-10 WOOT/Files/experiment.tex
Update case study

\subsection{Case study}
\label{subsec:case_study}

>>>>

\subsection{Case study}
\label{subsec:case_study}
\tool can be used in various attack scenarios, ranging from mobile devices to PC devices.
For example, \tool can be attached to the power station, which provides USB 3 hubs, in the airport to perform attacks.
Most people charge their laptops or smartphones in the power station in emergency, with negligence of security.
In the following paragraphs,
